What is happening on Twitter? A framework for student research projects with tweets

### 2020-06-13 Rmd/tweets-one.Rmd
submitted to JSE

```{r, recover-{{date}}}
fn <- paste0("../data/", "{{date}}", "-analyzed-tweet-ids.csv")
#fn <- paste0("../data/", "2020-05-10", "-analyzed-tweet-ids.csv")
tr_fn <- paste0("../data/", "{{date}}", "-rehydrated-tweets.rds")
#tr_fn <- paste0("../data/", "2020-05-10", "-rehydrated-tweets.rds")
sleep <- FALSE
if (!file.exists(tr_fn)){
  sleep <- TRUE
  tweets <- recover_stream(path = "{{tweet_json_file}}", verbose = TRUE) 
  #tweets <- recover_stream(path = "../data/2020-05-26 12:00:02-tweets.json", verbose = TRUE) 
  id_fn <- paste0("../data/tweets-status-ids-", "{{date}}", ".csv")
  #id_fn <- paste0("../data/tweets-status-ids-", "2020-05-26", ".csv")
  tweets %>%
    dplyr::select(status_id) %>%
    readr::write_csv(path = id_fn, 
                     col_names = FALSE)
  broken_ids <- readr::read_csv("broken_tweets.txt", col_names = FALSE) %>%
    dplyr::rename(status_id = X1) %>%
    dplyr::mutate(status_id = trimws(format(status_id, scientific = FALSE)))
  ids <- readr::read_csv(id_fn, col_names = FALSE) %>%
    dplyr::rename(status_id = X1) %>%
    dplyr::mutate(status_id = as.character(status_id))
  tweets_rehydrated1 <- rtweet::lookup_tweets(statuses = ids$status_id, 
                                              parse = TRUE)
  tweets_rehydrated2 <- rtweet::lookup_tweets(statuses = broken_ids$status_id, parse = TRUE)
  tweets_rehydrated <- tweets_rehydrated1 %>%
    dplyr::bind_rows(tweets_rehydrated2)
  # save ids of tweets that we actually used
  readr::write_csv(tibble::as_tibble(tweets_rehydrated$status_id), path = fn, col_names = FALSE)
  saveRDS(tweets_rehydrated, tr_fn)
} else {
  tweets_rehydrated <- readRDS(tr_fn)
}
```

>>>>

```{r, recover-{{date}}}
fn <- paste0("../data/", "{{date}}", "-analyzed-tweet-ids.csv")
tr_fn <- paste0("../data/", "{{date}}", "-rehydrated-tweets.rds")
sleep <- FALSE
if (!file.exists(tr_fn)){
  sleep <- TRUE
  tweets <- recover_stream(path = "{{tweet_json_file}}", verbose = TRUE) 
  id_fn <- paste0("../data/tweets-status-ids-", "{{date}}", ".csv")
  tweets %>%
    dplyr::select(status_id) %>%
    readr::write_csv(path = id_fn, 
                     col_names = FALSE)
  broken_ids <- readr::read_csv("broken_tweets.txt", col_names = FALSE) %>%
    dplyr::rename(status_id = X1) %>%
    dplyr::mutate(status_id = trimws(format(status_id, scientific = FALSE)))
  ids <- readr::read_csv(id_fn, col_names = FALSE) %>%
    dplyr::rename(status_id = X1) %>%
    dplyr::mutate(status_id = as.character(status_id))
  tweets_rehydrated1 <- rtweet::lookup_tweets(statuses = ids$status_id, 
                                              parse = TRUE)
  tweets_rehydrated2 <- rtweet::lookup_tweets(statuses = broken_ids$status_id, parse = TRUE)
  tweets_rehydrated <- tweets_rehydrated1 %>%
    dplyr::bind_rows(tweets_rehydrated2)
  # save ids of tweets that we actually used
  readr::write_csv(tibble::as_tibble(tweets_rehydrated$status_id), path = fn, col_names = FALSE)
  saveRDS(tweets_rehydrated, tr_fn)
} else {
  tweets_rehydrated <- readRDS(tr_fn)
}
```
